---
title: "R Note 3"
output: pdf_document
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Monte-carlo simulation to get a mean
* Many times it is very difficult to get a mean and variance analytically. In this case, we can use Monte carlo approach to calculate mean and variance. 

* Suppose we want to get mean and variance of $$x^3$$ where x follows normal(0,1). Following code run simulations to get this.


```{r e1, echo = TRUE}

nsim<-10000
x<-rnorm(nsim)
x3<-x^3
mean(x3)
sd(x3)

```

### COVID simulation 

* Consider the COVID simulation used in the previous note. Researchers want to mean and variance of new cases after 50 days (without social distancing, etc). 

* Analytically getting this is very difficult. But we can use Monte-carlo approach to get this easily


```{r e2, echo = TRUE}

Get_Trajectory<-function(){
  n_current_case<-10
  n_case_trajectory<-rep(0,11)
  n_case_trajectory[1]<-10
  for(i in 1:10){
    n_contact<-rpois(n_current_case,10)  
    n_new_case<-rbinom(n_current_case,n_contact, 0.2)
    n_current_case<-sum(n_new_case)
    n_case_trajectory[i+1]<-n_current_case
  }
  return(n_case_trajectory)
}

nsim<-100
out.all<-NULL
for(i in 1:nsim){
  out.all<-rbind(out.all, Get_Trajectory())
}

boxplot(out.all)

# Mean and se at 50 days
mean(out.all[,11])
sd(out.all[,11])
```
