---
title: "Note9"
output: pdf_document
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simulation data

We carry out simulation studies to investigate the behaviors of p-values. Consider a two group test, where each group has n=100 samples. Each sample in the first group follows N(0,1) and each sample in the second group follows N($\mu$, 1). The following code simulate one dataset with $\mu=0.5$

```{r pval}
set.seed(100)
WaldTest<-function(x1, x2){
  
  n1 = length(x1)
  n2 = length(x2)
  Mu1 = mean(x1)
  Mu2 = mean(x2)
  Var1 = mean((x1-Mu1)^2)
  Var2 = mean((x2-Mu2)^2)

  Theta = Mu2 - Mu1
  SE = sqrt(Var1/ n1 + Var2/n2)
  W = Theta/SE
  Pvalue = pchisq(W^2, df=1, lower.tail=FALSE)

  return(Pvalue)

}

mu<-0.5
n<-100
x1<-rnorm(n)
x2<-rnorm(n, mean = mu)

WaldTest(x1, x2)

```
### P-values under the null hypothesis

Now we generate 1000 datasets with $\mu=0$ and check the distribution of p-values. How does it look like?

```{r pval1}
mu<-0
nSIM<-1000
pval.all<-rep(0,nSIM)
for(i in 1:nSIM){

  x1<-rnorm(n)
  x2<-rnorm(n, mean = mu)

  pval.all[i]<-WaldTest(x1, x2)
  
}

hist(pval.all)
```
### Type I error rates

If we use $\alpha=0.05$ as a cutoff, how many p-valus are significant?

How about changing it to $\alpha=0.05/10, 0.05/1000$?


```{r pval2}
sum(pval.all < 0.05)
sum(pval.all < 0.05/10)
sum(pval.all < 0.05/1000)
```
### Power 

Researchers decide to use $\alpha=0.05/1000$, the bonferroni corrected alpha of testing 1000 hypothesis, as the cutoff. Now researchers want to check how the power changes by $\mu$. Carry out simulation studies with $\mu=0,0.1,...,1$

```{r power1}
mu.candidate<-0:10/10
nSIM<-1000
cutoff<-0.05/1000
Power.a<-rep(0,11)
for(j in 1:11){
  pval.all<-rep(0,nSIM)
  mu<-mu.candidate[j]
  
  for(i in 1:nSIM){

    x1<-rnorm(n)
    x2<-rnorm(n, mean = mu)

    pval.all[i]<-WaldTest(x1, x2)
  }
  Power.a[j]<-mean(pval.all < cutoff)
  
}

plot(mu.candidate, Power.a, type="b")
```


### Permutation test

Using the same simulation approach with $\mu=0.4$ carry out a permutation test with B=10000

```{r coris2}
set.seed(100)
mu<-0.4
n<-100
x1<-rnorm(n)
x2<-rnorm(n, mean = mu)
x<-c(x1,x2)

T.org<-mean(x1)-mean(x2)

# Permutation test
B<-10000
T.permu<-rep(0,B)
for(i in 1:B){
  idx_1<-sample.int(2*n, n)
  mu1<-mean(x[idx_1])
  mu2<-mean(x[-idx_1])
  T.permu[i]<-mu1-mu2
}

pval<-(sum(T.permu^2 >= T.org^2) +1)/(B+1)
pval

WaldTest(x1, x2)




```
