---
title: "Note6"
output: pdf_document
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coris data analysis 
It is well known that LDL (low density lipoprotein) is a bad cholesterol which increases the risk of coronary heart diseases (CHD). From the coris data analysis, we can show it. 
First we read the data and get summary statistics.

```{r coris}
df = read.table("./DATA/coris.txt", sep=",", header=TRUE)
df[1:2,]

# Change chd as a factor
df$chd = factor(df$chd)
table(df$chd)

par(mfrow=c(1,2))
hist(df$ldl, main="Histogram of LDL")
boxplot(df$ldl~ df$chd, main="LDL by CHD")
par(mfrow=c(1,1))

```
Get a little bit fancier plots using ggplot. 

```{r coris1}
library(ggplot2)
library(gridExtra)
library(dplyr)


# Violin plot
p1<-ggplot(df, aes(x=ldl, color=chd)) + geom_histogram(fill="white")
p2<-ggplot(df, aes(x=chd, y=ldl, color=chd)) + geom_violin() + 
	geom_boxplot(width=0.1)

grid.arrange(p1, p2, nrow = 1)

    
```

Following shows that empirical CDF of two groups are different.
```{r coris2}

eCDF_0<-ecdf(df$ldl[df$chd==0])
eCDF_1<-ecdf(df$ldl[df$chd==1])

x_range<-seq(min(df$ldl), max(df$ldl), length.out=1000)
plot(x_range, eCDF_0(x_range))
points(x_range, eCDF_1(x_range), col="red")
legend("topleft", legend=c("CHD=0", "CHD=1"), col=c("black", "red"), pch=1)    
    
```

Now we get the statistics. In particular, we get the mean LDL difference between two groups and its confidence interval. 

```{r coris3}
n0<-length(which(df$chd == 0))
n1<-length(which(df$chd == 1))


mu_0 = mean(df$ldl[df$chd==0])
mu_1 = mean(df$ldl[df$chd==1])
se_0 = sd(df$ldl[df$chd==0]) / sqrt(n0)
se_1 = sd(df$ldl[df$chd==1]) / sqrt(n1)

mu_0
mu_1
se_0
se_1

# Plug in estimator 
T = mu_1 - mu_0
T_se = sqrt(se_0^2 + se_1^2)  

T
T_se

# 95% interval
c(T - 1.96 * T_se, T + 1.96 * T_se)
```


