---
title: "Note10"
output: pdf_document
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coris data analysis

We carry out linear and logistic regressions using the coris data.

```{r coris}
df = read.table("./DATA/coris.txt", sep=",", header=TRUE)
head(df)
```
\vspace{1cm}


### Linear regression
In this analysis, we use ldl  as an outcome variable and age, tobacco, alcohol, adiposity, and obesity as predictors.

* Do predictors explain the ldl level?
* How much the ldl level would increase if the level of adiposity increases one unit?
* Which predictor is most significantly associated with ldl? 
* Is obesity significantly associated with ldl?

\vspace{5cm}

```{r coris3}
lm.out<-lm(ldl ~ age + tobacco + alcohol + adiposity + obesity, data=df )
summary(lm.out)


```

\vspace{3cm}

If adiposity is removed, how the result looks like?

```{r coris4}
lm.out<-lm(ldl ~ age + tobacco + alcohol  + obesity, data=df )
summary(lm.out)

```

###  Residual plots
To check whether linear regression assumptions are satisfied, draw residual plots
\vspace{3cm}
```{r coris5}

par(mfrow=c(2,2))
plot(lm.out)

```

### Logistic regression
Now we consider chd as the outcome and  age,  sbp, tobacco, ldl, adiposity, famhist, obesity and alcohol as predictor. Fit the logistic regression model.

\vspace{5cm}
```{r coris6}
glm.out <- glm(chd ~ age +  sbp+tobacco+ldl+adiposity+famhist+obesity+alcohol,  family=binomial, data=df)
summary(glm.out)
```

### Predicted logit and prob. 
Obtain predicted values as logit and prob scales. 
\vspace{3cm}
```{r coris7}
logit.predict<-predict(glm.out)
prob.predict<-exp(logit.predict)/(1+exp(logit.predict))

col<-c("blue", "red")
par(mfrow=c(1,3))

boxplot(logit.predict ~ df$chd, xlab="CHD" )
boxplot(prob.predict ~ df$chd, xlab="CHD" )

#plot(logit.predict, df$chd,  col=col[df$chd+1], pch="*", ylab="CHD")
#boxplot(pred_prob ~ df$chd, xlab="CHD", ylab="Prob")
plot(logit.predict, prob.predict, ylim=c(-0.1, 1.1) , col=col[df$chd+1] )


```
