---
title: "Note7"
output: pdf_document
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coris data analysis 
We use the same Coris data used in the previous chapter. Now we consider to get the distribution of median LDL for CHD=1

```{r coris}
df = read.table("./DATA/coris.txt", sep=",", header=TRUE)
LDL_1 = df$ldl[df$chd==1]
T_Median = median(LDL_1)

B<-1000
B_Median<-rep(0,B)
for(i in 1:B){
  B_sample<-sample(LDL_1, replace=TRUE)
  B_Median[i]<-median(B_sample)
}

hist(B_Median)

```

Now we get various Bootstrap confidence intervals

```{r coris1}

Get_CI<-function(T, B_Sample){
  
  # Percentile Interval
  CI_Percent = quantile(B_Sample, probs=c(0.025, 0.975))

  # Normal Interval
  se_b = sd(B_Sample)
  CI_Normal = c(T - 1.96* se_b, T + 1.96*se_b)

  # Pivot Interval
  CI_Pivot = c(2*T - CI_Percent[2], 2*T - CI_Percent[1])

  
  names(CI_Percent)<-c("2.5%", "97.5%")
  names(CI_Normal)<-c("2.5%", "97.5%")
  names(CI_Pivot)<-c("2.5%", "97.5%")

    re<-list(CI_Percent=CI_Percent, CI_Normal=CI_Normal, CI_Pivot=CI_Pivot)
  return(re)
  
}


Get_CI(T_Median, B_Median)
```

## LDL difference between CHD groups
Now we are interested in checking whether LDL levels are different by CHD groups. Here we use Bootstrap to get the confidence interval. 

```{r coris2}

n<-nrow(df)
T_MeanDiff = mean(df$ldl[df$chd==1]) - mean(df$ldl[df$chd==0])
T_MeanDiff

B<-1000
B_MeanDiff<-rep(0,B)
for(i in 1:B){
  B_sample_idx<-sample(1:n, replace=TRUE)
  df1<-df[B_sample_idx,]
  mean1<-mean(df1$ldl[df1$chd==1])
  mean0<-mean(df1$ldl[df1$chd==0])
  
  B_MeanDiff[i]<-mean1 - mean0
}

hist(B_MeanDiff)
# Confidence Interval
Get_CI(T_MeanDiff, B_MeanDiff)

```

## Correlation between LDL and sbp
Now researchers are interested in the correlation between LDL and sbp 

```{r coris3}

plot(df$ldl, df$sbp)
T_Corr<-cor(df$ldl, df$sbp)
T_Corr

n<-nrow(df)
B<-1000
B_Corr<-rep(0,B)
for(i in 1:B){
  B_sample_idx<-sample(1:n, replace=TRUE)
  df1<-df[B_sample_idx,]
  B_Corr[i]<-cor(df1$ldl, df1$sbp)
  
}

hist(B_Corr)
# Percentile Interval
Get_CI(T_Corr, B_Corr)


```


## Use boot package
Boot package can be used instead. Following code uses boot package to get a CI of the correlation between LDL and sbp 

```{r coris4}

library(boot)
CorrFunc <- function(d, indice, formula, resid, fit){   
	df1 = d[indice,]
	B_Corr<-cor(df1$ldl, df1$sbp)
	return(B_Corr)
}

boot.sample<-boot(df, CorrFunc, R=1000)
boot.sample

boot.ci(boot.sample)


```


