---
title: "R Note 2"
output: pdf_document
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Discrete random numbers
Following code generates 10 binomial random variables with different n and p
```{r e1, echo = TRUE}
nRandom<-10
n<-11:20
p<-seq(from=0.2, to=0.8, length.out=nRandom )

rbinom(nRandom, n,  p)
```
Following code generates 1000 poisson random variables with lambda=2
```{r e2, echo = TRUE}
nRandom<-1000
lambda<-2

out<-rpois(nRandom, lambda=lambda)
mean(out)
var(out)
hist(out)

```
Following code gets PMF and CDF

```{r e21, echo = TRUE}
dpois(3, lambda=2 )
ppois(3, lambda=2 )

```

### Continuous random variables
Following code generate 10000 (standard) Normal random variables with (mean=0, sd=1) and generate chi-square random variable 

```{r e3, echo = TRUE}
nRandom<-10000
Z<-rnorm(nRandom, mean=0, sd=1)
chi1<-Z^2

# compare them with random numbers from chi
chi2<-rchisq(nRandom, df=1)

# Use QQ plot to compare
qqplot(chi1, chi2)
abline(0,1)

# How about scatter plot?
plot(chi1,chi2, main="scatter plot")

```


### Simulation studies to predict number of new COVID infection
Researchers are interested in predicting the number of cases of COVID and the effect of the intervention measures and policies. To do this, we consider a following simulation scheme 

*	5 days as one-time unit. So 20 time units for 100 days 
* Initially there are 10 cases
* Each case has x close contacts in one-time unit, where x follows a Poisson distribution with lambda=10
* For each close contact, there is p=0.2 probability of the infection
* For simplicity, we consider that newly infected individual can only infect individuals in the next time unit (so only one time unit). It is similar after one-time unit, infected individuals are either detected/cured/died. 
* Do not consider a situation that infected individual has a close contact with already infected individual.

The following code run for 10 time units (50 days) to get trajectory of new cases.
```{r e4, echo = TRUE}
n_current_case<-10
n_case_trajectory<-rep(0,11)
n_case_trajectory[1]<-10
for(i in 1:10){
  n_contact<-rpois(n_current_case,10)  
  n_new_case<-rbinom(n_current_case,n_contact, 0.2)
  n_current_case<-sum(n_new_case)
  n_case_trajectory[i+1]<-n_current_case
}

plot(n_case_trajectory, type="l")
```

At day 50, people realize the severity of the problem and start to wash hand and wear a mask, which change p=0.14. Also government impose social distancing which changes lambda=3. Get the trajectory for the next 50 days

```{r e5, echo = TRUE}
n_case_trajectory_new<-rep(0,11)
n_case_trajectory_new[1]<-n_current_case
for(i in 1:10){
  n_contact<-rpois(n_current_case,3)  
  n_new_case<-rbinom(n_current_case,n_contact, 0.14)
  n_current_case<-sum(n_new_case)
  n_case_trajectory_new[i+1]<-n_current_case
}

plot(n_case_trajectory_new, type="l")
```
